### 2017-11-14 paper/sections/1_introduction.tex
paper: cleanup abstract and intro
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

Our analysis of the key-value activity generated by the ParSplice molecular
dynamics simulation demonstrates the need for more complex cache management
strategies. Baseline measurements show clear keyspace access patterns and hot
spots that offer significant opportunity for optimization. We use the data
management and policy engine from the Mantle system to dynamically explore a
variety of techniques, ranging from basic algorithms and heuristics to
statistical models, calculus, and machine learning. While Mantle was originally
designed for distributed file systems, we show how the collection of
abstractions effectively decomposes the problem into manageable policies for a
different domain and service.  Our exploration of this space results in a two
policy scheme that achieves 96\% efficiency while using only 7.6\% of the
memory resources required by the base case.

@@

In this paper, we design cache management policies for the ParSplice worker,
driven by a detailed analysis of the key-value accesses over the course of a
long running simulation across a variety of initial conditions. Our final
solution, shown by the ``Dynamically Sized Cache" line in
Figure~\ref{fig:cache-management}, detects keyspace access patterns and
re-sizes the cache accordingly. Without tuning or parameter sweeps, our
solution saves more memory than a hand-tuned cache without sacrificing
performance.  More importantly, it works for a variety initial conditions
without changing the policy itself.

>>>>

Our analysis of the key-value activity generated by the ParSplice molecular
dynamics simulation demonstrates the need for more complex cache management
strategies. Baseline measurements show clear keyspace access patterns and hot
spots that offer significant opportunity for optimization. We use the data
management and policy engine from the Mantle system to dynamically explore a
variety of techniques, ranging from basic algorithms and heuristics to
statistical models, calculus, and machine learning. While Mantle was originally
designed for distributed file systems, we show how the collection of
abstractions effectively decomposes the problem into manageable policies for a
different domain and service.  Our exploration of this space results in a
dynamically sized cache policy that, for our initial conditions, sacrifices
negligible performance while using only 28\% of the memory required by our
hand-tuned cache.

@@

In this paper, we design cache management policies for ParSplice, driven by a
detailed analysis of the key-value accesses over the course of a long running
simulation across a variety of initial conditions. The default ParSplice
implementation uses an unlimited sized cache, shown by the ``No Cache
Management" line Figure~\ref{fig:cache-management}. This solution is
unacceptable for HPC environments, where memory is precious and a common goal
is to keep memory for such data structures below 3\%\footnote{Empirically, we
find this threshold works well for most applications}.  While users can
configure ParSplice to resize the cache when it reaches a certain threshold,
this solution requires tuning and parameter sweeps; the dashed ``Cache (too
small)" curve in Figure~\ref{fig:cache-management} shows how a poorly
configured cache hurts performance.  Our final solution, shown by the
``Dynamically Sized Cache" line in Figure~\ref{fig:cache-management}, detects
keyspace access patterns and re-sizes the cache accordingly.  Without tuning or
parameter sweeps, our solution saves more memory than a hand-tuned cache
without sacrificing performance.  More importantly, it works for a variety
initial conditions without changing the policy itself.

### 2017-11-14 paper/sections/2_parsplice-keyspace-analysis.tex
paper: cleanup abstract and intro
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\subsubsection*{Experimental Setup} All experiments ran on Trinitite, a Cray
XC40 with 32 Intel Haswell 2.3GHz cores per node.  Each node has 128GB of RAM
and our goal is to limit the size of the cache to 3\% of
RAM\footnote{Empirically, we find this threshold works well for most
applications}. Note that this is an addition to the 30GB that ParSplice uses to
manage other ranks on the same node.  A single Cray node produced trajectories
that are \(5\times\) times longer than our 10 node CloudLab clusters and
\(25\times\) longer than our 10 node cluster at UCSC. As a result, it reaches
different job phases faster and gives us a more comprehensive view of the
workload. The performance gains compared to the commodity clusters have more to
do with memory/PCI bandwidth than network.

>>>>

\subsubsection*{Experimental Setup} All experiments ran on Trinitite, a Cray
XC40 with 32 Intel Haswell 2.3GHz cores per node.  Each node has 128GB of RAM
and our goal is to limit the size of the cache to 3\% of RAM . Note that this
is an addition to the 30GB that ParSplice uses to manage other ranks on the
same node.  A single Cray node produced trajectories that are \(5\times\) times
longer than our 10 node CloudLab clusters and \(25\times\) longer than our 10
node cluster at UCSC. As a result, it reaches different job phases faster and
gives us a more comprehensive view of the workload. The performance gains
compared to the commodity clusters have more to do with memory/PCI bandwidth
than network.
